Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-24 paper.tex
blame expressions were forgotten
typos in fig
partially revise sec2

\newcommand{\TOOdyn}[0]{\star}
\newcommand{\TOOpre}[1]{#1}
\newcommand{\POOunit}[0]{\mathtt{Unit}}
\newcommand{\POOfun}[2]{#1 \shortrightarrow #2}
\newcommand{\POOprod}[2]{#1 \times #2}
\newcommand{\POOsum}[2]{#1 \plus #2}
\newcommand{\eOOvar}[1]{#1}
\newcommand{\eOOsole}[0]{\mathtt{unit}}
\newcommand{\eOOlam}[4]{\lambda^{#1\rightarrow{}#2}#3.#4}
\newcommand{\eOOapp}[2]{(#1 \; #2)}
\newcommand{\eOOcons}[2]{\mathtt{cons} \; #1 \; #2}
\newcommand{\eOOcar}[1]{\mathtt{fst} \; #1}
\newcommand{\eOOcdr}[1]{\mathtt{snd} \; #1}
%\newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
%\newcommand{\eOOinr}[1]{\mathtt{inr} \; #1}
\newcommand{\eOOinl}[1]{\mathtt{inl} \; #1}
\newcommand{\eOOinr}[1]{\mathtt{inr} \; #1}
\newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}
\newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\cOOcast}[3]{#1 \Rightarrow^{#2} #3}
\newcommand{\oOOinj}{\mathtt{dyn}}
\newcommand{\oOOsole}{\mathtt{unit}}
\newcommand{\oOOfun}{\mathtt{fun}}
\newcommand{\oOOcons}{\mathtt{cons}}
\newcommand{\oOOinl}{\mathtt{inl}}
\newcommand{\oOOinr}{\mathtt{inr}}
\newcommand{\oOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\vOOcast}[2]{#1\langle#2\rangle}
\newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
\newcommand{\vOOtt}[0]{\mathtt{unit}}
\newcommand{\vOOcons}[2]{\mathtt{cons}\;#1\;#2}
\newcommand{\vOOinl}[1]{\mathtt{inl}\;#1}
\newcommand{\vOOinr}[1]{\mathtt{inr}\;#1}
%\newcommand{\rOOsucc}[1]{#1}
%\newcommand{\rOOfail}[1]{#1}
\newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
\newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}

\newcommand{\kOOmt}[0]{\mathtt{stop}}
\newcommand{\kOOconsI}[3]{[\mathtt{cons} \; \square \; \langle#1,#2\rangle ]#3}
\newcommand{\kOOconsII}[2]{[\mathtt{cons} \; #1 \; \square]#2}
\newcommand{\kOOinl}[1]{[\mathtt{inl}\; \square]#1}
\newcommand{\kOOinr}[1]{[\mathtt{inr}\; \square]#1}
\newcommand{\kOOappI}[3]{
  [\square \; \langle#1,#2\rangle]#3
}
\newcommand{\kOOappII}[2]{
  [#1 \; \square]#2}
\newcommand{\kOOcar}[1]{[\mathtt{fst} \; \square]#1}
\newcommand{\kOOcdr}[1]{[\mathtt{snd} \; \square]#1}
\newcommand{\kOOcaseI}[4]{
  [\mathtt{case} \; \square \; \langle#1,#3\rangle \; \langle#2,#3\rangle ]#4}
\newcommand{\kOOcaseII}[4]{
  [\mathtt{case} \; #1 \; \square \; \langle#2,#3\rangle ]#4}
\newcommand{\kOOcaseIII}[3]{
  [\mathtt{case} \; #1 \; #2 \; \square]#3}
\newcommand{\kOOcast}[2]{
  [\square \langle #1 \rangle]#2}

@@

\begin{figure}
  Syntax
  \[
  \begin{array}{rclr}
  \stxrule{T}{types}{
    \star \mid{}
    P
  }
  \stxrule{P}{pre-types}{
    \POOunit \mid
    \POOfun{T_1}{T_2} \mid
    \POOprod{T_1}{T_2} \mid
    \POOsum{T_1}{T_2}
  }
  \stxrule{e}{terms}{
    \eOOvar{x} \mid{}
    \eOOsole{} \mid{}
    \eOOlam{T_1}{T_2}{x}{e} \mid
    \eOOapp{e_1}{e_2} \mid
    \eOOcons{e_1}{e_2} \mid
    \eOOcar{e} \mid
    \eOOcdr{e}
  }
  \stxrulecont{
    \eOOinl{e} \mid
    \eOOinr{e} \mid
    \eOOcase{e_1}{e_2}{e_3} \mid
    \eOOcast{e}{T_1}{l}{T_2} \mid
    \eOOblame{l}
  }
  \end{array}
  \]

@@

The syntax and static semantics is the same for the \lazyD{} and
\lazyUD{} cast calculi, and is reviewed in \figref{fig:blame-static}.
As usual, the important features are the cast expressions,
$\eOOcast{e}{T_1}{l}{T_2}$, which are responsible for runtime type
checking, and blame expressions, $\eOOblame{l}$, that raise errors.
The syntax and static semantics is the same that of
\citet{siek2009exploring} except for a few minor exceptions:
\begin{itemize}
\item We add sum, product, and unit types.
\item We separate types into those with a type constructor at the top,
  the \emph{pretypes} ($\POOunit$, functions, products, and sums),
  versus the dynamic type $\star$ (a.k.a. $\mathtt{Dyn}$ or
  $\mathbb{?}$).
\item We annotate the codomain of a lambda abstraction explicitly
  because we refer to it in the dynamic semantics. 
\end{itemize}
As usual, the source $T_1$ and target types $T_2$ of a cast
$\eOOcast{e}{T_1}{l}{T_2}$ are required to be consistent, written $T_1
\sim T_2$. The consistency relation is standard and defined in
\figref{fig:blame-static}.

@@

\begin{figure}
  Machine state and other runtime data structures
  \[
  \begin{array}{rclr}
  \stxrule{v}{values}{
    \vOOtt{} \mid
    \vOOfun{\rho}{x}{e} \mid
    \vOOcons{v_1}{v_2} \mid
    \vOOinl{v} \mid
    \vOOinr{v} \mid   
    \vOOcast{v}{c}
  }
  \stxrule{c}{casts}{
    \cOOcast{T_1}{l}{T_2}
  }
  \stxrule{I}{injectable types (\lazyD)}{
    P
  }
  \stxrule{I}{injectable types (\lazyUD)}{
    \POOunit \mid
    \POOfun{\star}{\star} \mid
    \star \times \star \mid
    \star + \star
  }
  \stxrule{o}{observations}{
    \oOOinj \mid
    \oOOsole \mid
    \oOOfun \mid
    \oOOcons \mid
    \oOOinl \mid
    \oOOinr \mid
    \oOOblame{l}
  }
  \stxrule{r}{cast results}{
    \rOOsucc{v} \mid
    \rOOfail{l}
  }
  \stxrule{s}{states}{
    \sOOinspect{e}{\rho}{\kappa} \mid{}
    \sOOreturn{v}{\kappa} \mid{}
    \sOOhalt{o}
  }
  \stxrule{\kappa}{continuations}{
    \kOOmt \mid
    \kOOconsI{e}{\rho}{\kappa} \mid
    \kOOconsII{v}{\kappa} \mid
    \kOOinl{\kappa}
  }
  \stxrulecont{
    \kOOinr{\kappa} \mid
    \kOOappI{e}{\rho}{\kappa} \mid
    \kOOappII{v}{\kappa} \mid
    \kOOcar{\kappa}
  }
  \stxrulecont{ 
    \kOOcdr{\kappa}\mid
    \kOOcaseI{e}{e}{\rho}{\kappa}\mid
    \kOOcaseII{v}{e}{\rho}{\kappa}
  }
  \stxrulecont{
    \kOOcaseIII{v}{v}{\kappa} \mid
    \kOOcast{c}{\kappa}
  }
  \end{array}
  \]

@@

  Reduction \fbox{$\judgeCreduce{s}{s}$}
  \[
  \begin{array}{rclr}
    \hiredrule{
    \sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
  }{
    \sOOinspect{e}{\rho}{
      \kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa}
%     \langle\cOOcast{T_1}{l}{T_2}\rangle\kappa
    }
  }{}
  \redrule{
    \sOOinspect{\eOOvar{x}}{\rho}{\kappa}
  }{  
    \sOOreturn{\rho(x)}{\kappa}
  }{}
  \redrule{
    \sOOinspect{\eOOsole}{\rho}{\kappa}
  }{
    \sOOreturn{\vOOtt}{\kappa}
  }{}
  \redrule{
    \sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
  }{
    \sOOreturn{\vOOfun{\rho}{x}{e}}{\kappa}
  }{}
  \redrule{
    \sOOinspect{\eOOcons{e_1}{e_2}}{\rho}{\kappa}
  }{
    \sOOinspect{e_1}{\rho}{\kOOconsI{e_2}{\rho}{\kappa}}
  }{}
  \redrule{
    \sOOinspect{\eOOinl{e}}{\rho}{\kappa}
  }{
    \sOOinspect{e}{\rho}{\kOOinl{\kappa}}
  }{}
  \redrule{
  \sOOinspect{\eOOinr{e}}{\rho}{\kappa}
  }{
  \sOOinspect{e}{\rho}{\kOOinr{\kappa}}
  }{}
  \redrule{
    \sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
  }{
\sOOinspect{e_1}{\rho}{\kOOappI{e_2}{\rho}{\kappa}}}{}

@@

\redrule{
\sOOreturn{v_1}{\kOOconsI{e_2}{\rho}{\kappa}}}{
\sOOinspect{e_2}{\rho}{\kOOconsII{v_1}{\kappa}}}{}

\redrule{
\sOOreturn{v_2}{\kOOconsII{v_1}{\kappa}}}{
\sOOreturn{\vOOcons{v_1}{v_2}}{\kappa}}{}

\redrule{
\sOOreturn{v}{\kOOinl{\kappa}}}{
\sOOreturn{\vOOinl{v}}{\kappa}}{}

\redrule{
\sOOreturn{v}{\kOOinr{\kappa}}}{
\sOOreturn{\vOOinr{v}}{\kappa}}{}

@@

\begin{figure}
  Syntax
  \[
  \begin{array}{rclr}
% \stxrule{r}{cast results}{
%   \rOOsucc{v} \mid
%   \rOOfail{l}
% }
% \stxrule{s}{states}{
%   \sOOinspect{e}{\rho}{\kappa} \mid{}
%   \sOOreturn{v}{\kappa} \mid{}
%   \sOOhalt{o}
% }
  \stxrule{\kappa}{continuation}{
    \kOOcast{c}{k}
  }
  \stxrule{k}{pre-continuations}{
    \kOOmt \mid{}
    \kOOconsI{e}{\rho}{\kappa} \mid
    \kOOconsII{v}{\kappa} \mid
    \kOOinl{\kappa} \mid
    \kOOinr{\kappa}
  }
  \stxrulecont{
    \kOOappI{e}{\rho}{\kappa} \mid
    \kOOappII{v}{\kappa} \mid
    \kOOcar{\kappa} \mid
    \kOOcdr{\kappa}
  }
  \stxrulecont{
    \kOOcaseI{e}{e}{\rho}{\kappa} \mid
    \kOOcaseII{v}{e}{\rho}{\kappa} \mid
    \kOOcaseIII{v}{v}{\kappa}
  }
  \end{array}
  \]

@@

  Reduction \fbox{$\judgeSreduce{C}{s}{s}$}
  \[
  \begin{array}{rclr}
  \hiredruleS{
    \sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
  }{
    \sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
  }{}
  \redruleS{
    \sOOinspect{\eOOvar{x}}{\rho}{\kappa}
  }{  
    \sOOreturn{\rho(x)}{\kappa}
  }{}
  \redruleS{
    \sOOinspect{\eOOsole}{\rho}{\kappa}
  }{
    \sOOreturn{\hcvOOtt}{\kappa}
  }{}
  \hiredruleS{
    \sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
  }{
    \sOOreturn{\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)}}{\kappa}
  }{}
  \redruleS{
    \sOOinspect{\eOOcons{e_1}{e_2}}{\rho}{\kappa}
  }{
    \sOOinspect{e_1}{\rho}{
      wrap(\kOOconsI{e_2}{\rho}{\kappa})
    }
  }{}
  \redruleS{
    \sOOinspect{\eOOinl{e}}{\rho}{\kappa}
  }{
    \sOOinspect{e}{\rho}{wrap(\kOOinl{\kappa})}
  }{}
  \redruleS{
    \sOOinspect{\eOOinr{e}}{\rho}{\kappa}
  }{
    \sOOinspect{e}{\rho}{wrap(\kOOinr{\kappa})}
  }{}
  \redruleS{
    \sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
  }{
    \sOOinspect{e_1}{\rho}{wrap(\kOOappI{e_2}{\rho}{\kappa})}}{}

@@

  \redruleS{
    \sOOinspect{\eOOcase{e_1}{e_2}{e_3}}{\rho}{\kappa}}{
    \sOOinspect{e_1}{\rho}{wrap(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{}
  \hiredruleS{
    \sOOreturn{v}{\kOOcast{c}{k}}
  }{
  \begin{cases}
  \continue{k}{v'} & \sidecond{applyCast(v,c) = \rOOsucc{v'}} 
  \\
  \sOOhalt{\oOOblame{l}} & \sidecond{applyCast(v,c) = \rOOfail{l}}
  \end{cases}
  }{}
  \end{array}
  \]

@@

\funrule{
  \continue{v_1}{\kOOconsI{e_2}{\rho}{\kappa}}}{
  \sOOinspect{e_2}{\rho}{wrap(\kOOconsII{v_1}{\kappa})}}{}

\hifunrule{
  \continue{v_2}{\kOOconsII{v_1}{\kappa}}}{
  \sOOreturn{\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)}}{\kappa}}{}

\hifunrule{
  \continue{v}{\kOOinl{\kappa}}}{
  \sOOreturn{\hcvOOinl{v}{id(T)}}{\kappa}}{}

\hifunrule{
  \continue{v}{\kOOinr{\kappa}}}{
  \sOOreturn{\hcvOOinr{v}{id(T)}}{\kappa}}{}

>>>>

\newcommand{\TOOdyn}[0]{\star}
\newcommand{\TOOpre}[1]{#1}
\newcommand{\POOunit}[0]{\mathtt{Unit}}
\newcommand{\POOfun}[2]{#1 \shortrightarrow #2}
\newcommand{\POOprod}[2]{#1 \times #2}
\newcommand{\POOsum}[2]{#1 \plus #2}
\newcommand{\eOOvar}[1]{#1}
\newcommand{\eOOsole}[0]{\mathtt{unit}}
\newcommand{\eOOlam}[4]{\lambda^{#1\rightarrow{}#2}#3.#4}
\newcommand{\eOOapp}[2]{(#1 \; #2)}
\newcommand{\eOOcons}[4]{\mathtt{cons}^{\POOprod{#1}{#2}} \; #3 \; #4}
\newcommand{\eOOcar}[1]{\mathtt{fst} \; #1}
\newcommand{\eOOcdr}[1]{\mathtt{snd} \; #1}
\newcommand{\eOOinl}[3]{\mathtt{inl}^{\POOsum{#1}{#2}} \; #3}
\newcommand{\eOOinr}[3]{\mathtt{inr}^{\POOsum{#1}{#2}} \; #3}
\newcommand{\eOOcase}[3]{\mathtt{case} \; #1 \; #2 \; #3}
\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}
\newcommand{\eOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\cOOcast}[3]{#1 \Rightarrow^{#2} #3}
\newcommand{\oOOinj}{\mathtt{dyn}}
\newcommand{\oOOsole}{\mathtt{unit}}
\newcommand{\oOOfun}{\mathtt{fun}}
\newcommand{\oOOcons}{\mathtt{cons}}
\newcommand{\oOOinl}{\mathtt{inl}}
\newcommand{\oOOinr}{\mathtt{inr}}
\newcommand{\oOOblame}[1]{\mathtt{blame} \; #1}
\newcommand{\vOOcast}[2]{#1\langle#2\rangle}
\newcommand{\vOOfun}[3]{\mathtt{fun} \; #1 \; #2 \; #3}
\newcommand{\vOOtt}[0]{\mathtt{unit}}
\newcommand{\vOOcons}[2]{\mathtt{cons}\;#1\;#2}
\newcommand{\vOOinl}[1]{\mathtt{inl}\;#1}
\newcommand{\vOOinr}[1]{\mathtt{inr}\;#1}
\newcommand{\rOOsucc}[1]{\mathtt{succ}\;#1}
\newcommand{\rOOfail}[1]{\mathtt{fail}\;#1}

\newcommand{\kOOmt}[0]{\mathtt{stop}}
\newcommand{\kOOconsI}[5]{
	[\mathtt{cons}^{\POOprod{#1}{#2}} \; \square \; \langle#3,#4\rangle ]#5}
\newcommand{\kOOconsII}[4]{
	[\mathtt{cons}^{\POOprod{#1}{#2}} \; #3 \; \square]#4}
\newcommand{\kOOinl}[3]{[\mathtt{inl}^{\POOsum{#1}{#2}}\; \square]#3}
\newcommand{\kOOinr}[3]{[\mathtt{inr}^{\POOsum{#1}{#2}}\; \square]#3}
\newcommand{\kOOappI}[3]{
  [\square \; \langle#1,#2\rangle]#3
}
\newcommand{\kOOappII}[2]{
  [#1 \; \square]#2}
\newcommand{\kOOcar}[1]{[\mathtt{fst} \; \square]#1}
\newcommand{\kOOcdr}[1]{[\mathtt{snd} \; \square]#1}
\newcommand{\kOOcaseI}[4]{
  [\mathtt{case} \; \square \; \langle#1,#3\rangle \; \langle#2,#3\rangle ]#4}
\newcommand{\kOOcaseII}[4]{
  [\mathtt{case} \; #1 \; \square \; \langle#2,#3\rangle ]#4}
\newcommand{\kOOcaseIII}[3]{
  [\mathtt{case} \; #1 \; #2 \; \square]#3}
\newcommand{\kOOcast}[2]{
  [\square \langle #1 \rangle]#2}

@@

\begin{figure}
  Syntax
  \[
  \begin{array}{rclr}
  \stxrule{T}{types}{
    \star \mid{}
    P
  }
  \stxrule{P}{pre-types}{
    \POOunit \mid
    \POOfun{T}{T} \mid
    \POOprod{T}{T} \mid
    \POOsum{T}{T}
  }
  \stxrule{e}{terms}{
    \eOOvar{x} \mid{}
    \eOOsole{} \mid{}
    \eOOlam{T}{T}{x}{e} \mid
    \eOOapp{e}{e} \mid
    \eOOcons{T}{T}{e}{e} \mid
    \eOOcar{e} \mid
    \eOOcdr{e}
  }
  \stxrulecont{
    \eOOinl{T}{T}{e} \mid
    \eOOinl{T}{T}{e} \mid
    \eOOcase{e}{e}{e} \mid
    \eOOcast{e}{T}{l}{T} \mid
    \eOOblame{l}
  }
  \end{array}
  \]

@@

The syntax and static semantics is the same for the \lazyD{} and
\lazyUD{} cast calculi, and is reviewed in \figref{fig:blame-static}.
As usual, the important features are the cast expressions,
$\eOOcast{e}{T_1}{l}{T_2}$, which are responsible for runtime type
checking, and blame expressions, $\eOOblame{l}$, that raise errors.
The syntax and static semantics is the same that of
\citet{siek2009exploring} except for a few minor exceptions:
\begin{itemize}
\item We add sum, product, and unit types.
\item We separate types into those with a type constructor at the top,
  the \emph{pretypes} ($\POOunit$, functions, products, and sums),
  versus the dynamic type $\star$ (a.k.a. $\mathtt{Dyn}$ or
  $\mathbb{?}$).
\item We annotate the type of many expressions explicitly because we 
refer to them in the dynamic semantics. These expressions include cons 
expressions, left injections, right injections, and lambda abstractions.
\end{itemize}
As usual, the source $T_1$ and target types $T_2$ of a cast
$\eOOcast{e}{T_1}{l}{T_2}$ are required to be consistent, written $T_1
\sim T_2$. The consistency relation is standard and defined in
\figref{fig:blame-static}.

@@

\begin{figure}
  Machine state and other runtime data structures
  \[
  \begin{array}{rclr}
  \stxrule{v}{values}{
    \vOOtt{} \mid
    \vOOfun{\rho}{x}{e} \mid
    \vOOcons{v_1}{v_2} \mid
    \vOOinl{v} \mid
    \vOOinr{v} \mid   
    \vOOcast{v}{c}
  }
  \stxrule{c}{casts}{
    \cOOcast{T_1}{l}{T_2}
  }
  \stxrule{I}{injectable types (\lazyD)}{
    P
  }
  \stxrule{I}{injectable types (\lazyUD)}{
    \POOunit \mid
    \POOfun{\star}{\star} \mid
    \star \times \star \mid
    \star + \star
  }
  \stxrule{o}{observations}{
    \oOOinj \mid
    \oOOsole \mid
    \oOOfun \mid
    \oOOcons \mid
    \oOOinl \mid
    \oOOinr \mid
    \oOOblame{l}
  }
  \stxrule{r}{cast results}{
    \rOOsucc{v} \mid
    \rOOfail{l}
  }
  \stxrule{s}{states}{
    \sOOinspect{e}{\rho}{\kappa} \mid{}
    \sOOreturn{v}{\kappa} \mid{}
    \sOOhalt{o}
  }
  \stxrule{\kappa}{continuations}{
    \kOOmt \mid
    \kOOconsI{T_1}{T_2}{e}{\rho}{\kappa} \mid
    \kOOconsII{T_1}{T_2}{v}{\kappa} \mid
    \kOOinl{T_1}{T_2}{\kappa}
  }
  \stxrulecont{
    \kOOinr{T_1}{T_2}{\kappa} \mid
    \kOOappI{e}{\rho}{\kappa} \mid
    \kOOappII{v}{\kappa} \mid
    \kOOcar{\kappa}
  }
  \stxrulecont{ 
    \kOOcdr{\kappa}\mid
    \kOOcaseI{e}{e}{\rho}{\kappa}\mid
    \kOOcaseII{v}{e}{\rho}{\kappa}
  }
  \stxrulecont{
    \kOOcaseIII{v}{v}{\kappa} \mid
    \kOOcast{c}{\kappa}
  }
  \end{array}
  \]

@@

  Reduction \fbox{$\judgeCreduce{s}{s}$}
  \[
  \begin{array}{rclr}
    \hiredrule{
    \sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
  }{
    \sOOinspect{e}{\rho}{
      \kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa}
%     \langle\cOOcast{T_1}{l}{T_2}\rangle\kappa
    }
  }{}
  \redrule{
    \sOOinspect{\eOOvar{x}}{\rho}{\kappa}
  }{  
    \sOOreturn{\rho(x)}{\kappa}
  }{}
  \redrule{
    \sOOinspect{\eOOsole}{\rho}{\kappa}
  }{
    \sOOreturn{\vOOtt}{\kappa}
  }{}
  \redrule{
    \sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
  }{
    \sOOreturn{\vOOfun{\rho}{x}{e}}{\kappa}
  }{}
  \redrule{
    \sOOinspect{\eOOcons{T_1}{T_2}{e_1}{e_2}}{\rho}{\kappa}
  }{
    \sOOinspect{e_1}{\rho}{\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa}}
  }{}
  \redrule{
    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
  }{
    \sOOinspect{e}{\rho}{\kOOinl{T_1}{T_2}{\kappa}}
  }{}
  \redrule{
  \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
  }{
  \sOOinspect{e}{\rho}{\kOOinr{T_1}{T_2}{\kappa}}
  }{}
  \redrule{
    \sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
  }{
\sOOinspect{e_1}{\rho}{\kOOappI{e_2}{\rho}{\kappa}}}{}

@@

\redrule{
\sOOinspect{\eOOblame{l}}{\rho}{\kappa}}{
\sOOhalt{(\oOOblame{l})}}{}

\redrule{
\sOOreturn{v_1}{\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa}}}{
\sOOinspect{e_2}{\rho}{\kOOconsII{T_1}{T_2}{v_1}{\kappa}}}{}

\redrule{
\sOOreturn{v_2}{\kOOconsII{T_1}{T_2}{v_1}{\kappa}}}{
\sOOreturn{\vOOcons{v_1}{v_2}}{\kappa}}{}

\redrule{
\sOOreturn{v}{\kOOinl{T_1}{T_2}{\kappa}}}{
\sOOreturn{\vOOinl{v}}{\kappa}}{}

\redrule{
\sOOreturn{v}{\kOOinr{T_1}{T_2}{\kappa}}}{
\sOOreturn{\vOOinr{v}}{\kappa}}{}

@@

\begin{figure}
  Syntax
  \[
  \begin{array}{rclr}
% \stxrule{r}{cast results}{
%   \rOOsucc{v} \mid
%   \rOOfail{l}
% }
% \stxrule{s}{states}{
%   \sOOinspect{e}{\rho}{\kappa} \mid{}
%   \sOOreturn{v}{\kappa} \mid{}
%   \sOOhalt{o}
% }
  \stxrule{\kappa}{continuation}{
    \kOOcast{c}{k}
  }
  \stxrule{k}{pre-continuations}{
    \kOOmt \mid{}
    \kOOconsI{T_1}{T_2}{e}{\rho}{\kappa} \mid
    \kOOconsII{T_1}{T_2}{v}{\kappa} \mid
    \kOOinl{T_1}{T_2}{\kappa}
  }
  \stxrulecont{
  	\kOOinr{T_1}{T_2}{\kappa} \mid
    \kOOappI{e}{\rho}{\kappa} \mid
    \kOOappII{v}{\kappa} \mid
    \kOOcar{\kappa} \mid
    \kOOcdr{\kappa}
  }
  \stxrulecont{
    \kOOcaseI{e}{e}{\rho}{\kappa} \mid
    \kOOcaseII{v}{e}{\rho}{\kappa} \mid
    \kOOcaseIII{v}{v}{\kappa}
  }
  \end{array}
  \]

@@

  Reduction \fbox{$\judgeSreduce{C}{s}{s}$}
  \[
  \begin{array}{rclr}
  \hiredruleS{
    \sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
  }{
    \sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
  }{}
  \redruleS{
    \sOOinspect{\eOOvar{x}}{\rho}{\kappa}
  }{  
    \sOOreturn{\rho(x)}{\kappa}
  }{}
  \redruleS{
    \sOOinspect{\eOOsole}{\rho}{\kappa}
  }{
    \sOOreturn{\hcvOOtt}{\kappa}
  }{}
  \hiredruleS{
    \sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
  }{
    \sOOreturn{\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)}}{\kappa}
  }{}
  \redruleS{
    \sOOinspect{\eOOcons{T_1}{T_2}{e_1}{e_2}}{\rho}{\kappa}
  }{
    \sOOinspect{e_1}{\rho}{
      wrap(\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa})
    }
  }{}
  \redruleS{
    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
  }{
    \sOOinspect{e}{\rho}{wrap(\kOOinl{T_1}{T_2}{\kappa})}
  }{}
  \redruleS{
    \sOOinspect{\eOOinl{T_1}{T_2}{e}}{\rho}{\kappa}
  }{
    \sOOinspect{e}{\rho}{wrap(\kOOinr{T_1}{T_2}{\kappa})}
  }{}
  \redruleS{
    \sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
  }{
    \sOOinspect{e_1}{\rho}{wrap(\kOOappI{e_2}{\rho}{\kappa})}}{}

@@

  \redruleS{
    \sOOinspect{\eOOcase{e_1}{e_2}{e_3}}{\rho}{\kappa}}{
    \sOOinspect{e_1}{\rho}{wrap(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{}

\redruleS{
	\sOOinspect{\eOOblame{l}}{\rho}{\kappa}}{
	\sOOhalt{(\oOOblame{l})}}{}

  \hiredruleS{
    \sOOreturn{v}{\kOOcast{c}{k}}
  }{
  \begin{cases}
  \continue{k}{v'} & \sidecond{applyCast(v,c) = \rOOsucc{v'}} 
  \\
  \sOOhalt{\oOOblame{l}} & \sidecond{applyCast(v,c) = \rOOfail{l}}
  \end{cases}
  }{}
  \end{array}
  \]

@@

\funrule{
  \continue{v_1}{\kOOconsI{T_1}{T_2}{e_2}{\rho}{\kappa}}}{
  \sOOinspect{e_2}{\rho}{wrap(\kOOconsII{T_1}{T_2}{v_1}{\kappa})}}{}

\hifunrule{
  \continue{v_2}{\kOOconsII{T_1}{T_2}{v_1}{\kappa}}}{
  \sOOreturn{\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)}}{\kappa}}{}

\hifunrule{
  \continue{v}{\kOOinl{T_1}{T_2}{\kappa}}}{
  \sOOreturn{\hcvOOinl{v}{id(T_1)}}{\kappa}}{}

\hifunrule{
  \continue{v}{\kOOinr{T_1}{T_2}{\kappa}}}{
  \sOOreturn{\hcvOOinr{v}{id(T_2)}}{\kappa}}{}
